Soss

### 2019-12-30 paper/paper.tex
edits

\usepackage[ruled]{algorithm2e} 
%\usepackage{parskip}
\usepackage{backnaur}
\usepackage{jlcode}
\usepackage{todonotes}
% \usepackage{textalpha}
\usepackage{tikz}
\usetikzlibrary{bayesnet}

@@

\begin{tikzpicture}

@@

  \end{tikzpicture}

\begin{lstlisting}[language = Julia]

m = @model I,J begin
    α ~ HalfCauchy()
    σi ~ HalfNormal(α)
    σj ~ HalfNormal(α)

    εi ~ Normal(0, σi) |> iid(I)
    εj ~ Normal(0, σj) |> iid(J)
    yhat = εz .+ εy'
    σ ~ HalfNormal()
    y ~ For(I,J) do i,j 
            Normal(yhat[i,j], σ)
        end
end
\end{lstlisting}

@@

\begin{lstlisting}[language=julia]
struct Model{A,B,M} 
    args  :: Vector{Symbol}
    vals  :: NamedTuple
    dists :: NamedTuple
    retn  :: Union{Nothing, Symbol, Expr}
end
\end{lstlisting}

@@

\begin{lstlisting}[language = Julia]
  abstract type LCTerm end
  struct Lam{Arg, Body <: LCTerm} <: LCTerm end
  struct App{Fn<:LCTerm, Arg<:LCTerm} <: LCTerm end
  struct Var{N} <: LCTerm end

@@

  x = Core.Box()
  y = Core.Box()
  z = Core.Box()
  f(x) = (x, z)
  @assert (@lc x => x)(x) === (@lc y => y)(x)
  @assert (@lc f => x => f(x))(f)(y) === (y, z)
  \end{lstlisting}

>>>>

\usepackage[ruled]{algorithm2e} 
%\usepackage{parskip}
\usepackage{backnaur}
% \usepackage{jlcode}  
\usepackage{todonotes}
% \usepackage{textalpha}
\usepackage{tikz}
\usetikzlibrary{bayesnet}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[utf8x]{inputenc}
\usepackage{textgreek}
\usepackage{minted}

@@

\begin{figure}[H]
    \centering

    \begin{subfigure}[b]{0.4\textwidth}
        \begin{tikzpicture}

@@

        \end{tikzpicture}
        \caption{}
    \end{subfigure}
    \hspace{0.1in}
    \begin{subfigure}[b]{0.4\textwidth}

    \begin{minted}{julia}
    m = @model I,J begin
        α ~ HalfCauchy()
        σi ~ HalfNormal(α)
        σj ~ HalfNormal(α)

        εi ~ Normal(0, σi) |> iid(I)
        εj ~ Normal(0, σj) |> iid(J)
        yhat = εz .+ εy'
        σ ~ HalfNormal()
        y ~ For(I,J) do i,j 
                Normal(yhat[i,j], σ)
            end
        end
    \end{minted} 
    \caption{}
    \end{subfigure}

    \caption{A plate diagram (a) and Soss encoding (b) for a two-way analysis of variance model}
    \label{}
\end{figure}

@@

\begin{minted}{julia}
struct Model{A,B,M} 
    args  :: Vector{Symbol}
    vals  :: NamedTuple
    dists :: NamedTuple
    retn  :: Union{Nothing, Symbol, Expr}
end
\end{minted}

@@

\begin{minted}{julia}
  abstract type LCTerm end
  struct Lam{Arg, Body <: LCTerm} <: LCTerm end
  struct App{Fn<:LCTerm, Arg<:LCTerm} <: LCTerm end
  struct Var{N} <: LCTerm end

@@

  x = Core.Box()
  y = Core.Box()
  z = Core.Box()
  f(x) = (x, z)
  @assert (@lc x => x)(x) === (@lc y => y)(x)
  @assert (@lc f => x => f(x))(f)(y) === (y, z)
  \end{minted}
